Generating the Blueprints of the Java Ecosystem

### 2015-02-26 msr.tex
added import-process illustration

Initially, a snapshot (January 2012) of the Maven repository was downloaded locally. The repository contains various projects and their releases. A project version can be uniquely identified by the following triplet: {\it group id}, {\it artifact id} and {\it version}. The Maven repository contains several versions of each project.

All versions were filtered out and only the latest was kept. For each version in the Maven repository, each binary {\sc jar} file is accompanied by another {\sc jar}, which contains the source code. Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus. It included 12,959 projects, % dimitro@bkarak: this is a different number from the one at the table.
with more than 110 million lines of code. Overall the dataset contains almost 33 million unique measurements.

>>>>

The dataset construction process is illustrated in Figure~\cite{}.

\begin{figure}
\centering
\includegraphics[scale=0.5]{import-process}
\caption{}
\end{figure}

Initially, a snapshot of the Maven repository was downloaded locally. The repository contains various projects and their releases. A project version can be uniquely identified by the following triplet: {\it group id}, {\it artifact id} and {\it version}. The Maven repository contains several versions of each project.

All versions were filtered out and only the latest was kept. For each version in the Maven repository, each binary {\sc jar} file is accompanied by another {\sc jar}, which contains the source code. Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus. It included 11,365 projects, with more than 110 million lines of code. Overall the dataset contains almost 33 million unique measurements.
